The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-05-17 ms/ms.tex
Updates from Overleaf
overleaf

\begin{figure}[h]
\centering
\includegraphics[width=35pc]{../figs/violins.pdf}
\caption{Distributions of global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. See Section \ref{sect:exps} for scenario descriptions.}
\label{fig:violins}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Each point represents a simulation within the PPE. Points are spaced horizontally to minimize overlap.}
\label{fig:violins}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/violins.png}
\caption{Global annual gross primary production (GPP) and net ecosystem production (NEP) across the PPE within each of our six forcing scenarios. Each point represents a simulation within the PPE. Points are spaced horizontally to minimize overlap.}
\label{fig:violins}
\end{figure}
